%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Simon-Pierre Boucher} % Your name
\address{ 1820 rue des intendants, App. 218 \\ Québec, QC G1J5C2} % Your address
\address{(418)~$\cdot$~570~$\cdot$~1340 \\ simon-pierre.boucher.1@ulaval.ca} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Laval University, Quebec} \hfill {\em 2019-present} \\ 
Doctorate in Administrative Sciences - Finance and Insurance (Ph.D.) 
\smallskip 

{\bf Laval University, Quebec} \hfill {\em 2017-2018} \\ 
Master of Science in Administration - Finance (M. Sc)
\smallskip 

{\bf Laval University, Quebec} \hfill {\em 2013-2017} \\ 
Bachelor of Business Administration - Finance (B.A.A.)
\smallskip 
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Laval University}{2021 - present}{Teaching}{Quebec, QC}
\item GSF-3100 Capital market (Fall/Winter 2021, Fall 2022, Winter 2023)
\item GSF-6053 Financial Econometrics (Winter 2022)
\item GSF-1500 Financial Management (Summer 2022)
\item GSF-6028 Financial Theory (Winter 2024)
\end{rSubsection}


%------------------------------------------------


\begin{rSubsection}{Laval University}{2018 - 2021}{Graduate Teaching Assistant}{Quebec, QC}
\item GSF-2101 Portfolio Management
\item GSF-6025 Financial Strategies and Policies I
\item GSF-6008 Corporate finance
\item GSF-2102 Corporate finance
\item GSF-6028 Financial Theory
\end{rSubsection}

\begin{rSubsection}{Laval University}{2017 - 2021}{Graduate Research Assistant}{Quebec, QC}
\item Real estate database creation
\item Hedonic modeling
\item Literature review on financial problematics
\item Program econometric regression models on R, SAS, MATLAB.
\end{rSubsection}

%------------------------------------------------
\end{rSection}


\begin{rSection}{Research projects}
\begin{itemize}
\item Boucher, Simon-Pierre and Gagnon, Marie-Hélène and Power, Gabriel, Has Financialization Changed the Impact of Macro Announcements on Us Commodity Markets? (May 6, 2022). Available at SSRN: https://ssrn.com/abstract=4009292 or http://dx.doi.org/10.2139/ssrn.4009292
\item Boucher, Simon-Pierre and Gagnon, Marie-Hélène and Power, Gabriel, Modelling Volatility Dynamics Between Commodity ETFs and Their Net Asset Value using BVAR and HAR Models (January 2023)
\item Boucher, Simon-Pierre and Gagnon, Marie-Hélène and Power, Gabriel, Assessing the Efficacy of Intraday Volatility Measures in Response to Unexpected Macroeconomic Announcements (November 2023)
\end{itemize}
\end{rSection}

\begin{rSection}{Seminar or conference}
\begin{itemize}
\item CRREP presentation day, january 2022, Centre de recherche sur les risques, les enjeux économiques et les politiques publiques. 
\begin{itemize}
    \item Boucher, Simon-Pierre and Gagnon, Marie-Hélène and Power, Gabriel, Has Financialization Changed the Impact of Macro Announcements on Us Commodity Markets? (May 6, 2022). 
\end{itemize}
\item CRREP presentation day, may 2023, Centre de recherche sur les risques, les enjeux économiques et les politiques publiques. 
\begin{itemize}
    \item Boucher, Simon-Pierre and Gagnon, Marie-Hélène and Power, Gabriel, Modelling Volatility Dynamics Between Commodity ETFs and Their Net Asset Value using BVAR and HAR Models (January 2023)
\end{itemize}

\item 61nd Annual Meeting
Canadian Society for Economics, may 2022
\begin{itemize}
    \item Boucher, Simon-Pierre and Gagnon, Marie-Hélène and Power, Gabriel, Has Financialization Changed the Impact of Macro Announcements on Us Commodity Markets? (May 6, 2022). 
\end{itemize}
\item 62nd Annual Meeting
Canadian Society for Economics, may 2023
\begin{itemize}
    \item Boucher, Simon-Pierre and Gagnon, Marie-Hélène and Power, Gabriel, Modelling Volatility Dynamics Between Commodity ETFs and Their Net Asset Value using BVAR and HAR Models (January 2023)
\end{itemize}
\item 7th Commodity Markets Winter Workshop, Mont-Tremblant, January 2024.
\begin{itemize}
    \item Boucher, Simon-Pierre and Gagnon, Marie-Hélène and Power, Gabriel, Modelling Volatility Dynamics Between Commodity ETFs and Their Net Asset Value using BVAR and HAR Models (January 2023)
\end{itemize}
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & SAS, R, MatLab, STATA, Python, SQL, Latex, \\
 & Julia, Matematica Wolfram, C++, HTML, CSS, JAVA SCRIPT \\
Application & Github, Huuging Face, Databrick, Jupyther notebook\\
 & Quarto, Annaconda, R studio, Gitlab \\
Databases & COMPUSTAT, CRSP, Bloomberg, Morningstar, Thomson Reuters \\
\end{tabular}

\end{rSection}



%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
